Wall-to-wall mapping of peat depth from Lidar terrain and airborne radiometrics in Norwegian landscapes

### 2024-11-21 ms/ms.Rmd
ms: results - minor edit

For Ørskogfjellet, the best predictor configuration was *terrain and DMK*, followed by *terrain-only*.
Adding radiometric predictors to these configurations worsened model performance, especially in terms of concordance correlation and R^2^.
By itself, *DMK class* produced a concordance correlation coefficient of 0.17, but the worst RMSE of any model: \unit{98\,cm}.

>>>>

For Ørskogfjellet, the best predictor configuration was *terrain and DMK*, followed by *terrain-only*.
Adding radiometric predictors to these configurations worsened model performance, especially in terms of concordance correlation and R^2^.
By itself, *DMK class* produced a concordance correlation coefficient of 0.17 (compared to 0.008 at Skrimfjella), but the worst RMSE of any model at either site: \unit{98\,cm}.

### 2024-11-21 ms/ms.tex
ms: results - minor edit

For Ørskogfjellet, the best predictor configuration was \emph{terrain and DMK}, followed by \emph{terrain-only}.
Adding radiometric predictors to these configurations worsened model performance, especially in terms of concordance correlation and R\textsuperscript{2}.
By itself, \emph{DMK class} produced a concordance correlation coefficient of 0.17, but the worst RMSE of any model: \unit{98\,cm}.

>>>>

For Ørskogfjellet, the best predictor configuration was \emph{terrain and DMK}, followed by \emph{terrain-only}.
Adding radiometric predictors to these configurations worsened model performance, especially in terms of concordance correlation and R\textsuperscript{2}.
By itself, \emph{DMK class} produced a concordance correlation coefficient of 0.17 (compared to 0.008 at Skrimfjella), but the worst RMSE of any model at either site: \unit{98\,cm}.
